---
title: "my title"
author: "Dummy Surname (dummy@mail.com)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"      
output:
  html_document:
    toc: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1

**Build a Random Forest model to classify COVID-19 severity**

Using the training cohort provided in Supplementary Table 3, build a Random Forest classification model similar to the one in the publication to distinguish between non-Severe and Severe COVID-19 patients.

Report the following performance metrics from cross-validation:

-   Confusion matrix\
-   Accuracy\
-   ROC curve and AUC

How well does the Random Forest model separate non-Severe from Severe patients based on proteomic profiles?

```{r}

```

# Exercise 2

**Identify and interpret the most important features**

Using the trained Random Forest model from Exercise 1, identify the 25 most important protein features contributing to the classification. Disccus their biological relevance.

Compare your selected features to the proteins reported by the authors in Supplementary Table 5.

```{r}

```

# Exercise 3

**External prediction on an independent test cohort**

Using the final Random Forest model trained on the full training cohort, predict disease severity for patients in the independent test cohort provided in Supplementary Table 4.

Your task is to:

-   Apply the trained model to the test cohort.  
-   Obtain predicted probabilities of Severe disease for each patient.  
-   Assign predicted class labels based on these probabilities.  
-   Compare predictions to the true clinical labels.  


How does the model perform on the independent test cohort?

```{r}

```

# session info {.unnumbered}

```{r, results='asis',  echo=FALSE, message=FALSE }
sessionInfo()
```
